% Dissertation on cometric association schemes
%
%  B G Kodalen

\documentclass[12pt]{article}
\usepackage{longtable}
\input{preamble}

\usepackage{graphicx,amsthm,fullpage} 
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{setspace}
\usepackage{units}
\usepackage[mathscr]{euscript}
\usepackage{arydshln}
\usepackage{array}
\usepackage{bbm}
\usepackage{enumitem}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{scalefnt}
\usepackage{setspace}
\usepackage{bbm}
\usepackage{multicol}


%\usepackage{showlabels}
\usepackage{thmtools}
\usepackage{thm-restate}
\usepackage{comment}
\usepackage{float}
\usepackage{lmodern}

\usepackage{epigraph}



%\usepackage[symbols,nogroupskip,sort=none]{glossaries-extra}

%\input{symbols}

\newcommand{\vnorm}[1]{\left\|#1\right\|}
\newcommand*{\swap}[2]{#2#1}
\newcommand{\PLH}{{\mkern-2mu\times\mkern-2mu}}
\newcommand{\bigslant}[2]{{\left.\raisebox{.2em}{$#1$}\middle/\raisebox{-.2em}{$#2$}\right.}}


\makeatletter
\newenvironment{chapquote}[2][2em]
{\setlength{\@tempdima}{#1}%
	\def\chapquote@author{#2}%
	\parshape 1 \@tempdima \dimexpr\textwidth-2\@tempdima\relax%
	\itshape}
{\par\normalfont\hfill--\ \chapquote@author\hspace*{\@tempdima}\par\bigskip}
\makeatother
%%% CS Template

\setlength{\textheight}{8.63in}
\setlength{\textwidth}{6.3in}
\setlength{\topmargin}{-0.2in}
\setlength{\oddsidemargin}{0.1in}
\setlength{\evensidemargin}{0.1in}
\setlength{\headsep}{0.0in}

\newcommand{\brk}{\vspace*{0.18in}}
\newcommand{\smlbrk}{\vspace*{0.04in}}

%%% End template


%%% Connectivity commands
\newcommand{\m}{{{24}}}  % Special for this paper, subscripts and superscripts {24}
\newcommand{\IP}{{\rm IP}}
\newcommand{\re}{{\mathbb R}}
\newcommand{\ints}{{\mathbb Z}}
\newcommand{\A}{{\bf A}}
\newcommand{\B}{{\bf B}}
\newcommand{\E}{{\mathsf E}}
\newcommand{\cE}{{\mathcal E}}  % Euclidean space
\newcommand{\F}{{\mathcal F}}
\newcommand{\G}{{\mathcal G}}
\newcommand{\I}{{\mathsf I}}
\newcommand{\tI}{\tilde{I}}
\newcommand{\J}{{\mathsf J}}
\renewcommand{\L}{\boldsymbol{\wedge}}  % Leech lattice in \sf font
\newcommand{\Z}{{\mathsf Z}}
\newcommand{\cI}{{\mathcal I}}
\newcommand{\cJ}{{\mathcal J}}
\renewcommand{\S}{{\mathsf S}}
\newcommand{\cT}{{\mathcal T}}
\newcommand{\tU}{\tilde{U}}
\newcommand{\bv}{{\mathbf v}}
\newcommand{\tW}{\tilde{W}}
\newcommand{\X}{{\mathcal X}}
\newcommand{\cZ}{{\mathcal Z}}
\newcommand{\QI}{{\mathcal Q}{\mathcal I}}
\newcommand{\Nm}{{\sf Nm}}
\newcommand{\cP}{{\mathcal P}}
\newcommand{\one}{{\mathbf 1}}
\newcommand{\dis}{\displaystyle}

\DeclareMathOperator\Rad{Rad}
\DeclareMathOperator\colsp{colsp}
\DeclareMathOperator\nullsp{nullsp}
\DeclareMathOperator\diam{diam}
\DeclareMathOperator\mult{mult}
%%% End connectivity


\newcommand{\bb}{\mathbf{b}}
\newcommand{\bw}{\mathbf{w}}
\newcommand{\bx}{\mathbf{x}}

\newcommand{\sA}{\mathsf{A}}
\newcommand{\sB}{\mathsf{B}}
\newcommand{\sF}{\mathsf{F}}
\newcommand{\sS}{\mathsf{S}}
\newcommand{\sQ}{\mathsf{Q}}


\newcommand{\scR}{\mathscr{R}}


\newcommand{\BMA}{\mathbb{A}}
\newcommand{\BMB}{\mathbb{B}}
\newcommand{\BMC}{\mathbb{C}}
\newcommand{\bbF}{\mathbb{F}}
\newcommand{\bbL}{\mathbb{L}}
\newcommand{\bbR}{\mathbb{R}}
\newcommand{\bbZ}{\mathbb{Z}}
\newcommand{\bbQ}{\mathbb{Q}}

\newcommand{\cM}{\mathcal{M}}
\newcommand{\cN}{\mathcal{N}}
\newcommand{\cR}{\mathcal{R}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cG}{\mathcal{G}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cx}{\mathbb{C}}

\newcommand{\ones}{\mathbf{1}}

\newcommand{\dash}{\hdashline[2pt/2pt]}

\renewcommand{\vec}[1]{\mathbf{#1}}

\graphicspath{{Figures/}}

\DeclareMathOperator{\tr}{tr}
\DeclareMathOperator{\spn}{span}
\DeclareMathOperator{\rank}{rank}
\DeclareMathOperator{\srg}{srg}
\DeclareMathOperator{\Mat}{\mathsf{Mat}}

%\newenvironment{my_enumerate}{
%\begin{enumerate}
%  \setlength{\itemsep}{1pt}
%  \setlength{\parskip}{0pt}
%  \setlength{\parsep}{0pt}}{\end{enumerate}
%}



\newtheorem*{thm*}{Theorem}
\newtheorem{thm}{Theorem}[chapter]
\newtheorem{lem}[thm]{Lemma}
\newtheorem{prop}[thm]{Proposition}
\newtheorem{cor}[thm]{Corollary}
\newtheorem*{remark}{Remark}
\newtheorem*{conj*}{Conjecture}
\newtheorem{conj}[thm]{Conjecture}
\theoremstyle{definition}
\newtheorem{example}{Example}[chapter]
\newtheorem*{definition}{Definition}

\newcommand\abstractname{Abstract}  %%% here
\makeatletter
\if@titlepage
\newenvironment{abstract}{%
	\thispagestyle{plain}
	\null\vfil
	\@beginparpenalty\@lowpenalty
	\begin{center}%
		\bfseries \abstractname
		\@endparpenalty\@M
\end{center}}%
{\par\vfil\null}
\else
\newenvironment{abstract}{%
	\if@twocolumn
	\section*{\abstractname}%
	\else
	\small
	\begin{center}%
		{\bfseries \abstractname\vspace{-.5em}\vspace{\z@}}%
	\end{center}%
	\quotation
	\fi}
{\if@twocolumn\else\endquotation\fi}
\fi
\makeatother


\usepackage{hyperref}
\usepackage{cleveref}
%\doublespacing

\usepackage{makeidx}
%\usepackage{showidx}
%\let\oldindex\index
%\renewcommand{\index}[1]{\oldindex{#1}\marginpar{\small#1}}
\makeindex



%\title{\textbf{Cometric Association Schemes}}
\author{Brian G. Kodalen}
\date{}
\begin{document}

	\begin{center}
		
		{\large\textbf{Cometric Association Schemes}}
		
		
		by
		
		\smlbrk
		Brian G.\ Kodalen
		
		\smlbrk\smlbrk
		A Thesis
	
		
		Submitted to the Faculty
		
		
		of the 
		
		
		WORCESTER POLYTECHNIC INSTITUTE
		
		
		In partial fulfillment of the requirements for the
		
		
		Degree of Doctor of Philosophy
		
		
		in
		
		
		Mathematical Sciences
		
		
		by
		
		\brk\brk
		\rule{3in}{1.2pt}
		
		\smlbrk
		March 2019
	\end{center}
\vfill
APPROVED:

{\setlength{\parindent}{0cm}
\begin{center}
\vspace{0.4in}
\rule{3in}{0.8pt}

% Change this to your favorite CS professor.
Dr.\ William J.\ Martin\\ Major Thesis Advisor
\end{center}
\vspace{0.4in}
\rule{3in}{0.8pt}\hfill\rule{3in}{0.8pt}

% This is also constant :)
Dr.\ Peter J.\ Cameron\hfill Dr. Padraig \'{O} Cath\'{a}in\\University of St Andrews\hfill Worcester Polytechnic Institute

\vspace{0.4in}
\rule{3in}{0.8pt}\hfill\rule{3in}{0.8pt}

% This is also constant :)
Dr. Peter R. Christopher\hfill Dr. William M. Kantor\\Worcester Polytechnic Institute \hfill University of Oregon

\vspace{0.4in}
\rule{3in}{0.8pt}\hfill\rule{3in}{0.8pt}

% This is also constant :)
Dr. G\'{a}bor N. S\'{a}rk\"{o}zy\hfill Dr. Luca Capogna\\Worcester Polytechnic Institute\hfill Worcester Polytechnic Institute\\\hspace*{\fill} Head of Department

}
% end of titlepage
\clearpage

%\doublespacing

\begin{abstract}
	\thispagestyle{plain}
	
	The combinatorial objects known as association schemes arise in group theory, extremal graph theory, coding theory, the design of experiments, and even quantum information theory. One may think of a $d$-class association scheme as a $(d+1)$-dimensional matrix algebra over $\mathbb{R}$ closed under entrywise products. In this context, an imprimitive scheme is one which admits a subalgebra of block matrices, also closed under the entrywise product. Such systems of imprimitivity provide us with \textit{quotient schemes}, smaller association schemes which are often easier to understand, providing useful information about the structure of the larger scheme.
	
	One important property of any association scheme is that we may find a basis of $d+1$ idempotent matrices for our algebra. A \textit{cometric} scheme is one whose idempotent basis may be ordered $E_0,E_1,\dots,E_d$ so that there exists polynomials $f_0,f_1,\dots,f_d$ with $f_i\circ(E_1) = E_i$ and $\text{deg}(f_i) = i$ for each $i$. Imprimitive cometric schemes relate closely to $t$-distance sets, sets of unit vectors with only $t$ distinct angles, such as equiangular lines and mutually unbiased bases. Throughout this thesis we are primarily interested in three distinct goals: building new examples of cometric association schemes, drawing connections between cometric association schemes and other objects either combinatorial or geometric, and finding new realizability conditions on feasible parameter sets --- using these conditions to rule out open parameter sets when possible.
	
	After introducing association schemes with relevant terminology and definitions, this thesis focuses on a few recent results regarding cometric schemes with small $d$. We begin by examining the matrix algebra of any such scheme, first looking for low rank positive semidefinite matrices with few distinct entries and later establishing new conditions on realizable parameter sets. We then focus on certain imprimitive examples of both 3- and 4-class cometric association schemes, generating new examples of the former while building realizability conditions for both. In each case, we examine the related $t$-distance sets, giving conditions which work towards equivalence; in the case of 3-class $Q$-antipodal schemes, an equivalence is established. We conclude by partially extending a result of Brouwer and Koolen concerning the connectivity of graphs arising from metric association schemes.
\end{abstract}
\clearpage
%	\begin{itemize}[label={}]
%		\itemsep-.5em
%		\item Dr. Peter J. Cameron, Queen Mary, University of London
%		\item Dr. Padraig \'{O} Cath\'{a}in, WPI
%		\item Dr. Peter R. Christopher, WPI
%		\item Dr. William M. Kantor, University of Oregon
%		\item Dr. William J. Martin, WPI (Advisor)
%		\item Dr. G\'{a}bor N. S\'{a}rk\"{o}zy, WPI
%	\end{itemize}


\vfill
\begin{center}
	\textbf{Acknowledgments}
\end{center}

First and foremost, I would like to thank my advisor Dr.\ William Martin. The guidance he gave over the last five years has made me a better instructor, writer, researcher, and student. His patience, understanding, and willingness to read every line of this document and many others was essential to my success at WPI. The sheer enjoyment he finds in this subject, paired with his knowledge of many neighboring areas, drew me to this field originally and spurred me on throughout the more frustrating times --- instilling the same love for association schemes within me.

\brk

I would also like to thank those with whom I have had numerous conversations throughout my time at WPI, helping to teach me a broader picture of discrete math. Specifically Dr.\ William Kantor, Dr.\ Tyler Reese, Dr.\ Padraig \'{O} Cath\'{a}in, Dr.\ Peter Christopher, Dr.\  G\'{a}bor N. S\'{a}rk\"{o}zy, and Mike Yereniuk, all of whom have challenged me to step out of my comfort zone to tackle problems in nearby topics. I am additionally thankful to Dr.\ Peter Cameron for agreeing to serve on my dissertation committee along with many of those mentioned above. I am also grateful to the math department at WPI as a whole for the encouragement and support which has characterized my time at WPI.

\brk

Finally, I would like to thank those who have kept me together the last five years. My Mom and Dad, whose love, encouragement, and support has built me into the man I am today. My wife Cara for laughing when I wasn't funny, nodding along when I wasn't making sense, and pushing me forward whenever I was ready to quit. My pastor Neal who took a personal interest in my well-being and met with me consistently as both a counselor and friend. And finally, my Lord and Savior Jesus Christ, without whom I would be lost.
 
 \vfill
 \clearpage

	\tableofcontents
	%\listoffigures
	%\listoftables
	\clearpage
	\input{symbols}
	\clearpage
	

	
	\mainmatter
	%\pagenumbering{arabic}
	%\setcounter{page}{1}
	
	\input{introduction}
	\input{association}
	\input{psdcone}
	%\input{schoenberg}
	\input{3-class}
	\input{4-class}
	\input{connectivity}
	
	\appendix
	\input{appendix}
	
	\singlespacing %For the bibliography
	%\nocite{*}
	\addcontentsline{toc}{chapter}{Bibliography}
	\bibliographystyle{abbrv}
	\bibliography{Dissertation}
	\addcontentsline{toc}{chapter}{Index}
	\printindex
\end{document}
